Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-05-26 paper.tex
Add Evan's responses to TODO notes (email Feb 28, 2018) through [88]

\subsubsection*{Acknowledgements}
This research is supported in part by the Joint Institute for Nuclear
Astrophysics---Center for the Evolution of the Elements (JINA-CEE)
and the National Science Foundation under grant numbers X,
and the U.S.\ Department of Energy, Office of Science, Office of Nuclear Physics,
under Award Number DE-FG02-02ER41216.
\footnote{TODO (all): grant nos?}
We thank Sherwood Richers for providing his neutrino transport code
\lstinline{Sedonu} for comparisons,
Fran\c{c}ois H\'{e}bert for his timely help in finding and
correcting bugs in the time-interpolation algorithm,
and Luke Roberts for helpful discussions.

@@

Each source term is unique to the neutrino or antineutrino species modeled,
and consists of a sum over all of the processes contributing to that
category of interaction. For example:
$C^{\nu_e}_{{\rm AE}} = \sum_i\,C^{\nu_e}_{{\rm AE},i}$,
where $i$ labels the absorption/emission processes involving $\nu_e$
in Tab.~\ref{tab:neutrino_processes}.
By contrast $C^{\nu_x}_{{\rm AE}} = 0$,
\footnote{TODO (Evan, Brett): note that we use a nonzero $C^{\nu_x}_{{\rm AE}}$}
where $\nu_x$ stands for any of the four heavy-lepton neutrinos and
antineutrinos.

We compute our rates using the open source neutrino interaction
library \lstinline{NuLib}~\footnote{\url{http://www.nulib.org}}.
We compile a table of sources defined over the four dimensions of
density, temperature, electron-fraction, and neutrino energy, and
interpolate quad-linearly to the points sampled along each ray.

>>>>

\subsubsection*{Acknowledgements}
This research is supported in part by the Joint Institute for Nuclear
Astrophysics---Center for the Evolution of the Elements (JINA-CEE)
and the National Science Foundation under grant numbers \lstinline{X} (MBD),
by NASA through the Hubble Fellowship under grant \lstinline{51344.001-A},
awarded by the Space Telescope Science Institute,
which is operated  by the Association of Universities for Research in Astronomy, Inc.,
for NASA under contract \lstinline{NAS 5-26555} (EO),
and through the U.S.\ Department of Energy, Office of Science, Office of Nuclear Physics,
under award number \lstinline{DE-FG02-02ER41216} (GCM).
\footnote{TODO (Matt, Francois): grant nos?}
We thank Sherwood Richers for providing his neutrino transport code
\lstinline{Sedonu} for comparisons,
Fran\c{c}ois H\'{e}bert for his timely help in finding and
correcting bugs in the time-interpolation algorithm,
and Luke Roberts for helpful discussions.

@@

We compute our rates using the open source neutrino interaction
library \lstinline{NuLib} \cite{ocon2015-gr1d_with_nu}.
We compile a table of sources defined over the four dimensions of
density, temperature, electron-fraction, and neutrino energy, and
interpolate quad-linearly to the points sampled along each ray.

Each source term is unique to the neutrino or antineutrino species modeled,
and consists of a sum over all of the processes contributing to that
category of interaction. For example:
$C^{\nu_e}_{{\rm AE}} = \sum_i\,C^{\nu_e}_{{\rm AE},i}$,
where $i$ labels the absorption/emission processes involving $\nu_e$
in Tab.~\ref{tab:neutrino_processes}.
By contrast $C^{\nu_x}_{{\rm AE}}$ is formally equal to zero.
However, in practice, \lstinline{NuLib} implements the thermal pair processes
via an effective emission/absorption term in order to avoid the need
to couple energy groups and species (see Sec.~\ref{ssec:sources_pp}).
This has been shown to work well for core-collapse supernovae
\cite{ocon2015-gr1d_with_nu}.
